Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Update comment

@@

\noindent This can be used to document and test arbitrary Monoid
instances, the specification from above would become:

@@

\begin{quote}
    TBD: state that ``A library for reusable pieces of specification would be
    useful.''
\begin{itemize}
    \item
        In Section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
      \item copied here from Section~\ref{sec:reuseable-pecs}:
        We should ensure the practicality of reusable spec and
        prepare reusable spec to cover variety of type classes.

>>>>

\begin{quote}
    TBD: We read both, stdout + stderr from GHCi and compare that with the
    expected result.  On Windows, only stdout works (IIRC, when an
    example causes output to stderr on windows, doctest exits with an
    error, see http://hackage.haskell.org/trac/ghc/ticket/5761).

    sol: relevant?
\end{quote}

@@

\noindent This can be used to document and test arbitrary Monoid
instances.
The specification from above becomes:

@@

\begin{quote}
    TBD: state that ``A library for reusable pieces of specification would be
    useful.''
\begin{itemize}
    \item
        In Section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
      \item copied here from Section~\ref{sec:reuseable-pecs}:

        Reusable spec is an idea to scrap boilerplate of evidence.
        For instance, without reusable spec,
        each developer of an instance of a type class should
        express evidence for its laws.
        Since instances of a type class share API,
        we can avoid such boilerplate.
        The following is an example to implement
        evidence for Monoid laws:

        We should ensure the practicality of reusable spec and
        prepare reusable spec to cover variety of type classes.
